\section{Before You Begin}
Verify the following before installing the pilot package.

\begin{longtable}{@{}p{0.28\textwidth}p{0.66\textwidth}@{}}
\toprule
\textbf{Required item} & \textbf{What the user needs} \\
\midrule
Installer & \code{EMA_AI_Professional_Setup_1.0.0-dev.2-unsigned.exe} \\
Revit project & \textbf{MEP-NISD-MIDDLE SCHOOL} project access in Revit \\
Owner Requirements workbook & \code{NORTHWEST ISD 06.02.2025.xlsx} \\
Revit version & One of the validated Revit years: 2022--2027 \\
Feedback form access & Permission to open and submit the Google Form \\
Internet access & Required only to download the installer and submit feedback \\
Docker & Not required for the \textbf{EMA AI Revit Pilot} profile \\
GPU & Not required for deterministic requirement checking \\
Disk space & Enough space for the installed add-in and local working files \\
Install permission & Permission to install add-ins in the user profile \\
\bottomrule
\end{longtable}

\begin{warnbox}{Compatibility note}
The repository validates support for Revit 2022 through 2027 in the shipped add-in payloads. Any newer or older year should be treated as unverified unless the release notes explicitly say otherwise.
\end{warnbox}

\subsection*{Installed files and profiles}
The current release packaging defines three client-facing profiles:
\begin{itemize}
  \item \textbf{Revit Add-in Only} - recommended for the controlled pilot
  \item \textbf{Pilot Core} - full local platform
  \item \textbf{Pilot Core + Local AI} - optional local AI on top of the full platform
\end{itemize}

\begin{tipbox}{Recommended pilot path}
For first-time users, choose \textbf{Revit Add-in Only}. The pilot guide does not require Docker, PostgreSQL, or local AI unless you were specifically instructed to install the full platform.
\end{tipbox}

\subsection*{Exact installer file}
Download only this approved file from the installer folder:
\begin{center}
\fcolorbox{EMA Blue}{EMA SoftBlue}{\parbox{0.92\textwidth}{\centering\code{EMA_AI_Professional_Setup_1.0.0-dev.2-unsigned.exe}}}
\end{center}

\subsection*{What not to do}
\begin{itemize}
  \item Do not choose the full local platform unless instructed.
  \item Do not select local AI unless explicitly requested.
  \item Do not install while Revit is open.
  \item Do not disable Application Control or antivirus if the file is blocked. Send a screenshot instead.
\end{itemize}
\clearpage
