\section{Review the Report}
The HTML report is the main review artifact. Start with the executive summary, then filter by discipline, status, or urgency, and then open a requirement card.

\subsection*{What to look for}
\begin{itemize}
  \item Executive summary
  \item Discipline filters
  \item Status filters
  \item Urgency
  \item Key issues
  \item Requirement cards
  \item Evidence found
  \item Missing information
  \item Revit Element IDs
  \item Recommended action
\end{itemize}

\subsection*{Requirement card anatomy}
\begin{infobox}{One requirement card}
\begin{tikzpicture}[font=\small, node distance=3mm]
  \node[draw,rounded corners,fill=white,minimum width=0.96\textwidth,minimum height=6.0cm,align=left,inner sep=4mm] (card) {};
  \node[anchor=north west] at ($(card.north west)+(4mm,-4mm)$) {\textbf{Requirement ID:} \code{REQ-101}};
  \node[anchor=north west] at ($(card.north west)+(4mm,-11mm)$) {\textbf{Requirement Text:} Provide panel and circuit assignment for lighting fixtures.};
  \node[anchor=north west] at ($(card.north west)+(4mm,-22mm)$) {\textbf{Status:} Not Met \hspace{1em} \textbf{Confidence:} 0.86 \hspace{1em} \textbf{Urgency:} Critical};
  \node[anchor=north west] at ($(card.north west)+(4mm,-33mm)$) {\textbf{Evidence Used:} 1 candidate element inspected. 0 element(s) already contain the required parameter data.};
  \node[anchor=north west] at ($(card.north west)+(4mm,-44mm)$) {\textbf{Missing Evidence:} Panel and circuit values};
  \node[anchor=north west] at ($(card.north west)+(4mm,-55mm)$) {\textbf{Next Best Action:} Assign panel and circuit values to the listed elements before the next deliverable.};
  \node[anchor=north west] at ($(card.north west)+(4mm,-66mm)$) {\textbf{Element IDs:} 123456, 123457, 123458};
\end{tikzpicture}
\end{infobox}

\subsection*{How to read the requirement card}
\begin{enumerate}
  \item \textbf{Requirement ID} is the primary identifier for feedback.
  \item \textbf{Requirement Text} is the workbook statement being checked.
  \item \textbf{Status} tells you the automated result.
  \item \textbf{Confidence} shows how strongly the deterministic check matched the available evidence.
  \item \textbf{Urgency} shows how quickly the team should review it.
  \item \textbf{Evidence Used} lists the model evidence the engine found.
  \item \textbf{Missing Evidence} tells you what is still absent.
  \item \textbf{Next Best Action} is the recommended follow-up.
  \item \textbf{Element IDs} are the Revit IDs you can use to locate the evidence in the model.
\end{enumerate}

\subsection*{How to open the report}
Use \textbf{Report Navigator} if your build includes the report window inside Revit. Use \textbf{Open Browser} if your build opens the latest report in the default browser. Both options are acceptable when available.

\subsection*{Report source}
The example report folder is here:
\begin{center}
\link{https://drive.google.com/drive/folders/1_b_eXT1muhlJ2Ytza267ZEXhCdizI3fq?usp=drive_link}
\end{center}

\subsection*{Status meanings}
\begin{longtable}{@{}p{0.24\textwidth}p{0.46\textwidth}p{0.22\textwidth}@{}}
\toprule
\textbf{Status} & \textbf{What it means} & \textbf{What the reviewer should do} \\
\midrule
Met & Available evidence appears to satisfy the requirement. & Confirm the evidence is correct. \\
Not Met & The requirement is evaluable and the evidence does not satisfy it. & Verify the gap and expected correction. \\
Needs Human Review & Engineering judgment or document evidence is required. & Identify the missing drawing, spec, or decision. \\
Insufficient Model Data & Required model information is missing. & Identify the missing parameter or model content. \\
Not Applicable & The requirement does not apply to the scope. & Confirm the scope exclusion. \\
\bottomrule
\end{longtable}

\begin{warnbox}{Pilot boundary}
These are pilot evaluation results. They do not represent engineering approval or compliance certification.
\end{warnbox}
\clearpage
